---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1




Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

```{r , include=FALSE}
# install.packages("remotes")
# install.packages("ggplot2")
library(classdata)
library(ggplot2)

str(ames)
head(ames)
names(ames)
```
## Variables (#1)
Variables include

- Parcel Id is a chr of id
- Address chr of address
- Style is a character fctr which is style of house
- Occupancy is a character fctr of occupancy
- Sale Date is a date of when sold
- Sale Price is a dbl of sale price
- Multi Sale chr of if sold multi or not
- Year Built int of when built
- Acres dbl of acre amount
- Total living Area int of total living area
- Bedrooms int of how many bedrooms
- FinishedBsmtAre is a dbl of total area of finished basement
- LotArea dbl of lot area in sq feet
- AC is logical value of if propertyh has ac
- FirePlace logical value of if has fire place
- Neighborhood factor variable of neighborhood area in ames
All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

Isabel's Work:
```{r}
library(ggplot2)
ggplot(ames, aes(x = Acres, y = `Sale Price`)) +
  geom_point() +
  labs(title = "Scatterplot")
```

- Most of the distribution in the scatterplot accross the x axis is between 0.0 and 2.5 acres. Although there are outlier oddities. If I were to take out outliers with high sales price or high acres, our dataset would be more clear to read. When observing the outliers, there isn't a correlation between price and acres. The acres with the highest count aren't high in price and vice versa for price. This leads me to believe that other variables are impacting this data.

## #4 Logan Pappas

- Range of Bedrooms variable -
```{r , include=TRUE}
range(ames$Bedrooms, na.rm = TRUE)
```
- Box Plot of Sale price compared to Bedrooms
```{r , include=TRUE}
ggplot(ames, aes(x = factor(Bedrooms), y = log10(`Sale Price`))) +
  geom_boxplot()

```

## Explanation

There are a few extreme outliers that are homes selling for several million dollars. This made most homes appear compressed near zero on the y-axis. Becuase of this I applied a log10 next to sales price to reveal a more of what the data shows. Homes with more bedrooms generally sold for more, but there was more variation within each category. Some 5+ bedroom homes sold for less than typical 3 or 4 bedroom homes, showing that other factors other than bedroom could influence price.




